Towards Automated Merging of Code Clones in Object-Oriented Programming Languages\\- Work in Progress -

### 2019-06-27 sattose/paper.tex
Restructuring, removing, redoing, etc paper

\subsubsection{Thresholds}\label{chap:thresholds}
CloneRefactor works on basis of three thresholds for finding clones:
\begin{enumerate}
  \item \textbf{Number of statements/declarations:} The number of statements/declarations that should be equal/similar for it to be considered a clone.
  \item \textbf{Number of tokens:} The number of tokens (excluding whitespace, end-of-line terminators and comments) that should be equal/similar for it to be considered a clone.
  \item \textbf{Number of lines:} The minimum amount of lines (excluding lines that do not contain any tokens) that should be equal/similar for it to be considered a clone.
\end{enumerate}
Of course, if any threshold is set to zero, it will be ignored, thus not all thresholds have to be used at all times. We consider ``number of lines'' to be the least important, as it highly depends on the developer of the codebase (and we want to prevent this dependence). Empirical research indicates that setting the ``number of statements/declarations'' to 3 ensures that many non-harmful clones are filtered out, as lower thresholds detect many clones that pose no harm to the design of the code. On the downside, this also filters out some harmful antipatterns. For instance, if a cloned statement has many tokens we might want to consider it a clone even if it spans a single statement (as a cloned line with many tokens is more harmful than one with few).

The measurements in our study use the following thresholds:
\begin{itemize}
  \item \textbf{Number of statements/declarations:} 1
  \item \textbf{Number of tokens:} 12
  \item \textbf{Number of lines:} 1
\end{itemize}

>>>>

\subsubsection{Thresholds}\label{chap:thresholds}
CloneRefactor works on basis of three thresholds for finding clones:
\begin{enumerate}
  \item \textbf{Number of statements/declarations:} The number of statements/declarations that should be equal/similar for it to be considered a clone.
  \item \textbf{Number of tokens:} The number of tokens (excluding whitespace, end-of-line terminators and comments) that should be equal/similar for it to be considered a clone.
  \item \textbf{Number of lines:} The minimum amount of lines (excluding lines that do not contain any tokens) that should be equal/similar for it to be considered a clone.
\end{enumerate}
Of course, if any threshold is set to zero, it will be ignored, thus not all thresholds have to be used at all times. We consider ``number of lines'' to be the least important, as it highly depends on the developer of the codebase (and we want to prevent this dependence).
